Guided Proofreading of Automatic Segmentations for Connectomics\\~\\\textit{Supplemental Material}

### 2017-04-04 paper/arxiv/conclusion.tex
Latest updates including supplemental for submission and the arXiv versions.

%The task of automatic cell boundary segmentation is difficult, and trying to improve such segmentations automatically as a post-process through merge and split error correction is, in principle, no different than trying to improve the underlying cell boundary segmentation. Due to the task difficulty, manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. Humans are the bottleneck and minimizing the manual labor is the goal.
%We have trained classifiers to find merge and split errors in automatic segmentations of connectomics data. We then reduce the correction of these errors to simple yes/no decisions. This allows proofreading with better performance than existing systems.
%Our experiments also show that automatic proofreading works. This has the potential to further reduce the manual labor and will be the target of future research. To encourage testing of our proposed architecture and replication of our experiments, we provide our framework and data as free and open research at (link omitted for review).
%Minimizing manual labor is the goal when proofreading large automatic segmentations. Our classifiers suggest potential errors and corrections better than existing systems. This is especially important for novice users. Novices report difficulties when using fully interactive software but are invaluable to proofread the shear amounts of connectomics data.
%Our experiments also show that automatic proofreading works. This has the potential to further reduce human involvement and will be the target of future research. We provide our framework and data as free and open research at (link omitted for review).
Humans are the bottleneck when proofreading segmentation data and minimizing the manual labor is the goal. Our classifiers suggest potential errors and corrections better than existing methods. This reduces the time spent finding and correcting errors.
Our experiments also show that automatic proofreading has potential to further reduce human involvement. This will be the target of future research. We provide our framework and data as free and open research at (link omitted for review).

>>>>

Humans are the bottleneck when proofreading segmentation data and minimizing the manual labor is the goal. Our classifiers suggest potential errors and corrections better than existing methods. This reduces the time spent finding and correcting errors.
Our experiments also show that automatic proofreading has potential to further reduce human involvement. This will be the target of future research. We provide our framework and data as free and open research at \url{http://rhoana.org/guidedproofreading/}.

\section*{Acknowledgements}
We would like to thank Stephen Plaza for detailed explanations of focused proofreading and Toufiq Parag for the configuration of the NeuroProof classifier.

### 2017-04-04 paper/arxiv/evaluation.tex
Latest updates including supplemental for submission and the arXiv versions.

%\begin{figure*}[t]
%\begin{center}
%\includegraphics[width=\linewidth]{gfx/results_mouse.png}
%\end{center}
%  \vspace{-4mm}
%   \caption{Performance evaluation of the classifiers on two mouse brain datasets measured as adapted Rand error (lower scores are better). We compare guided proofreading (GP), guided proofreading with active label suggestion (GP*) and focused proofreading. Proofreading is performed automatically (autom., with probability threshold $p_t=.95$), simulated as a perfect user (sim.), or by novice and expert users as indicated. The first row of images shows the results of a user study and includes comparisons to the interactive proofreading software Dojo by Haehn \etal \cite{haehn_dojo_2014}. GP* is able to correct the segmentation further than other methods. The second row shows the results of the simulated user compared to automatic GP* and FP performance. The bottom right graph compares automatic GP* and simulated GP* per individual correction. The blue dashed line here indicates the moment the probability threshold $p_t$ is reached. The simulated user is able to correct the initial segmentation beyond this threshold while automatic GP* then introduces errors.}
%\label{fig:results_mouse}
%\end{figure*}

@@

%\paragraph{CREMI A/B/C.} As part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI), six ssTEM datasets were made publicly available\footnote{\scriptsize{\url{http://www.cremi.org}}},  each $1250\times1250\times125$ voxels. Since only three datasets include manually-labeled `ground truth', we use these three volumes for our experiments. The volumes are part of an adult fruit fly (Drosophila melanogaster) brain. The resolution of all three datasets is $4\times4\times40~\text{nm}^3\text{/voxel}$.

@@

\begin{table}[t]
\caption{Training parameters, cost, and results of our guided proofreading classifier versus focused proofreading by Plaza~\cite{focused_proofreading}. Both methods were trained on the same mouse brain dataset using the same hardware (Tesla X GPU).}%While the training of our classifier is more expensive, testing accuracy is superior. }

\small{
\begin{tabular}{ll}
	\toprule
	\begin{tabular}{l}
		\textbf{Guided Proofreading} \\ \midrule
		\emph{Parameters} \\ \midrule
		Filter size: 3x3 \\ No. Filters 1: 64 \\ No. Filters 2--4: 48 \\ Dense units: 512 \\ Learning rate: 0.03--0.00001\\ Momentum: 0.9--0.999\\Mini-Batchsize: 128 \\
	\end{tabular}
	&
	\begin{tabular}{l}
		\vspace{0.2mm} \\
		\midrule
		\emph{Results---Test Set} \\ \midrule Cost [m]: 383 \\ Val. loss: 0.0845 \\ Val. acc.: 0.969 \\ Test. acc.: 0.94 \\ Prec./Recall: 0.94/0.94 \\ F1 Score: 0.94 \\ ~ \\
	\end{tabular}
\end{tabular}

\vspace{0.5mm}
\begin{tabular}{ll}
	\toprule
	\begin{tabular}{l}
		\textbf{Focused Proofreading}\\ \midrule
		\emph{Parameters} \\ \midrule
		Iterations: 3 \\
		Learning strategy: 2\\
		Mito agglomeration: Off~~~~~~ \\  % Crappy alignment spacing
		Threshold: 0.0\\~\\
	\end{tabular}
	&
	\begin{tabular}{l}
		\vspace{0.2mm} \\
		\midrule
		\emph{Results---Test Set} \\ \midrule Cost [m]: 217 \\ Val. acc.: 0.99 \\ Test. acc.: 0.68 \\ Prec./Recall: 0.58/0.56 \\ F1 Score: 0.54 \\
	\end{tabular}
%	\bottomrule
\end{tabular}
\hrule
}
\label{tab:parameters}
\end{table}

@@

Each study session began with a five minute standardized explanation of the task. Then, the participants were asked to perform a 3 minute proofreading task on separate but representative data using focused proofreading. The participants were allowed to ask questions during this time. The classifier did not matter in this case since the user interface was the same. The experimenter then loaded the AC4 subvolume with initial pre-computed classifications by either guided proofreading or focused proofreading depending on assignment. After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation~\cite{NASATLX}.
\begin{figure*}[t]
\centering
\includegraphics[width=\linewidth]{gfx/ac4trails_combined.pdf}
\caption{Performance comparison of Plaza's focused proofreading (red) and our guided proofreading (blue) on the AC4 subvolume. All measurements are reported as median VI, the lower the better. We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (green line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle. In all cases, guided proofreading yields better results with fewer corrections.}
\label{fig:ac4trails}
\end{figure*}

@@

\paragraph{Evaluation metric.} We measure the similarity between proofread segmentations and the manual `ground truth' labelings using \textit{variation of information} (VI). VI is a measure of the distance between two clusterings, closely related to mutual information (the lower, the better).% We treat VI as a continuous variable during analysis.

%For baseline comparison, we also list the parameters and training results of focused proofreading in this table but elaborate on these further in section \ref{sec:evaluation}.

%
%\begin{table}[h]
%%\resizebox{\textwidth}{!}{%
%\tiny
%\begin{tabular}{@{}c|c|c|c|c|c|c@{}}
%& \textbf{cost [m]} & \textbf{Val. loss} & \textbf{Val. acc.} & \textbf{Test acc.} & \textbf{Prec./Recall} & \textbf{F1 Score} \\
%\hspace{1mm}
%\begin{tabular}{@{}l@{}}
%\textbf{Guided Proofreading} \\ Filter size: 3x3 \\ No. Filters 1: 64 \\ No. Filters 2-4: 48 \\ Dense units: 512 \\ Learning rate: 0.03-0.00001\\ Momentum: 0.9-0.999\\Mini-Batchsize: 128\\~\\
% \end{tabular}
% & 383  & 0.0845  & 0.969  & 0.94  & 0.94/0.94  & 0.94 \\
%\hline
%\begin{tabular}{@{}l@{}}
%\\
%\textbf{Focused Proofreading} \\
%Iterations: 3 \\
%Learning strategy: 2\\
%Mito agglomeration: Off\\
%Threshold: 0.2
% \end{tabular}
% & 43  & ?  & ?  & 0.839  & ?/?  & ? \\
%\end{tabular}
%\vspace{1mm}
%\caption{Training parameters, cost and results of our guided proofreading classifier versus focused proofreading by Plaza \cite{focused_proofreading}. Both methods were trained on the same mouse brain dataset using the same hardware (Tesla K40 graphics card). While the training of our classifier is more expensive, testing accuracy is superior. }
%\label{tab:parameters}
%\end{table}

%For performance comparison on data of a different species, in particular on fruitfly brain (drosophila), we retrain our network. The training procedure is according to our initial training and network architecture as well as parameters are not changed. We further elaborate on the drosophila datasets in section~\ref{sec:evaluation}. Fig.~\ref{fig:roc} displays receiver operating characteristics (ROC) for  guided proofreading trained on mouse and drosophila data, as well as our comparison baseline focused proofreading trained on these datasets respectively.
%
%\begin{figure}[h]
%  \vspace{-5mm}
%\begin{center}
%  \includegraphics[width=\linewidth]{gfx/roc.pdf}
%\end{center}
%  \vspace{-10mm}
%   \caption{ROC performance of guided proofreading (GP) and focused proofreading (FP) trained separately on mouse and drosophila brain images. The area under the curve indicates better performance for GP.}
%\label{fig:roc}
%\end{figure}

%\subsection{Mouse Brain}
%
%Mouse brain is a common target for connectomics research because the structural proportions are similar to human brains~\cite{jeff_science}. For our first experiment we recruited novice and expert participants as part of a quantitative user study. Our second experiment is performed on a larger dataset and we evaluate a simulated user.
%\\~\\
%\textbf{User study.} Recently, Haehn \etal evaluated the interactive proofreading tools Raveler, Mojo, and Dojo as part of an experiment with novice users~\cite{haehn_dojo_2014}. The participants corrected an automatic segmentation with merge and split errors. The dataset was the most representative sub-volume (based on object size histograms) of a larger connectomics dataset and $400x400x10$ voxels in size. The participants were given a fixed time frame of 30 minutes to perform the correction interactively. While participants clearly struggled with the proofreading task, the best performing tool in their evaluation was Dojo. The dataset including manually labeled ground truth and the results of Haehn \etal are publicly available. This means we are able to use their findings as a baseline for comparison of GP for novices. In particular, we use the best performing user of Dojo who was truly an outlier as reported by Haehn \etal.
%
%Since interactive proofreading most likely yields lower performance than aided proofreading, we also compare against FP by Plaza~\cite{focused_proofreading} which is integrated in Raveler and freely available. For FP we consulted an expert to obtain the best possible parameters as shown in table \ref{tab:parameters}. Besides performance by novices, we are also interested in expert proofreading performance. Therefore, we design between-subjects experiments for 20 novice users and separately, for 6 expert users using the exact same conditions as Haehn \etal. The recruiting, consent and debriefing process is further described in the supplementary material. We randomly assign 10 novices to GP with active label suggestion (GP*) and 10 novices to FP. For the expert experiment, we assign accordingly.
%In addition to human performance, we also evaluate automatic GP, automatic GP with active label suggestion (GP*) and automatic FP. Due to the automatic nature, we do not enforce the 30 minute time limit but we stop once our probability threshold of $p_t=.95$ is reached. This value was observed as stable in previous experiments using automatic GP (see supplementary material). To measure proofreading performance in comparison to ground truth, we use the adapted Rand error (aRE) metric~\cite{RAND}. aRE is a measure of dissimilarity, related to introduced errors, meaning lower scores are better.
%
%The results of our comparisons are shown in the first row of Fig.~\ref{fig:results_mouse}. In all cases, GP* is able to correct the segmentation further than other methods (aRE measures: automatic GP XX, GP* XX, FP XX, novice Dojo XX, GP* XX, FP XX, expert Dojo XX, GP* XX, FP XX). This is not surprising since guided proofreading works for both merge and split errors while FP does not and in interactive Dojo the majority of time is spent finding errors which is minimized for aided proofreading solutions. In fact, the average correction time for novices is for GP* 3.6 (expert X), for FP Y (expert YY), and for Dojo 30 (expert ZZ) seconds.
%\\~\\
%\textbf{Simulated experiment.} For our second experiment with mouse brain data, we proofread the last 50 slices of the blue 3-cylinder mouse cortex volume of Kasthuri \etal~\cite{kasthuri2015saturated} which we also used for testing in section~\ref{sec:methods}. The data was not seen by the network before and includes $2048x2048x50$ voxels with a total number of 17,560 labeled objects. Since an interactive evaluation of such a large dataset would consume a significant amount of time, we restrict our experiment to a simulated (perfect) user and to automatic corrections, both with GP, GP* and FP. Similar to our comparison study, the simulated user assess a stream of errors by comparing the adapted Rand error measure before and after each performed correction. The simulated user is designed to be perfect and only accepts corrections if the measure is reduced. This time, we do not enforce a time limit to see the lower bound of possible corrections. For automatic GP and GP*, we use our defined probability threshold $p_t=.95$.
%
%The results of this experiment are shown in the second row of Fig.~\ref{fig:results_mouse}. GP* is again able to correct the segmentation further than other methods (aRE measures: automatic GP XX, GP* XX, FP XX, simulated GP* XX, FP XX). Again, the results are not surprising since GP* can correct merge and split errors.
%
%\subsection{Drosophila Brain}
%
%The drosophila brain is analyzed by connectomics researchers because of its small size and hence, a reasonable target to obtain a complete wiring diagram. Despite the size, fruit flies exhibit complex behaviors and are in general well studied. We evaluate the performance of our guided proofreading classifiers on three different datasets of adult fly brain. The datasets are publicly available as part of the MICCAI 2016 challenge on circuit reconstruction from electron microscopy images (CREMI)\footnote{The MICCAI CREMI challenge data is available at  http://www.cremi.org}. Each dataset consists of $1250x1250x125$ voxels of training data (A,B,C) as well as testing data (A+,B+,C+) of the same dimensions. Manually labeled ground truth is also available for A,B, and C but not for the testing data.
%
%Since drosophila brain exhibits different cell structures than mouse brain, we retrain the guided proofreading classifiers (and our automatic segmentation pipeline) as well as focused proofreading combined on the three training datasets. We use 300 slices of the A,B,C samples for training and validation, and 75 slices for testing. This results in YYY correct and ZZZ split error patches (respectively, XXX and YYY for testing). The architecture and all parameters of our classifiers stay the same. The trained GP classifier exhibits a reasonable performance on the testing data as seen in Fig.~\ref{fig:roc}.
%
%\begin{figure}[h]
%\begin{center}
%  \includegraphics[width=\linewidth]{gfx/results_fruitfly.png}
%\end{center}
%  \vspace{-4mm}
%   \caption{Results of guided proofreading with active label suggestion (GP*) and focused proofreading performed automatically on three drosophila datasets. The datasets are part of the MICCAI 2016 CREMI challenge and publicly available. We measure performance as adapted Rand error (the lower, the better). GP* is able to correct the initial segmentation further than FP. Our GP* scores places us XXnd on the CREMI leaderboard.}
%\label{fig:results_fruitfly}
%\end{figure}
%
%We then use the trained GP* and FP classifiers to evaluate proofreading automatically. Since ground truth labeling is not available, the evaluation is performed by submitting our results to the CREMI leaderboard. Again, we use adapted Rand error to quantify the performance. Fig.~\ref{fig:results_fruitfly} shows the results for each of the A+,B+, and C+ datasets. The performance of GP* is significantly better than FP and places us XXnd on the CREMI leaderboard.

>>>>

@@

@@

\begin{table}[t]
\caption{Training parameters, cost, and results of our guided proofreading classifier versus focused proofreading by Plaza~\cite{focused_proofreading}. Both methods were trained on the same mouse brain dataset using the same hardware (Tesla X GPU).}
\small{
\begin{tabular}{ll}
	\toprule
	\begin{tabular}{l}
		\textbf{Guided Proofreading} \\ \midrule
		\emph{Parameters} \\ \midrule
		Filter size: 3x3 \\ No. Filters 1: 64 \\ No. Filters 2--4: 48 \\ Dense units: 512 \\ Learning rate: 0.03--0.00001\\ Momentum: 0.9--0.999\\Mini-Batchsize: 128 \\
	\end{tabular}
	&
	\begin{tabular}{l}
		\vspace{0.2mm} \\
		\midrule
		\emph{Results---Test Set} \\ \midrule Cost [m]: 383 \\ Val. loss: 0.0845 \\ Val. acc.: 0.969 \\ Test. acc.: 0.94 \\ Prec./Recall: 0.94/0.94 \\ F1 Score: 0.94 \\ ~ \\
	\end{tabular}
\end{tabular}

\vspace{0.5mm}
\begin{tabular}{ll}
	\toprule
	\begin{tabular}{l}
		\textbf{Focused Proofreading}\\ \midrule
		\emph{Parameters} \\ \midrule
		Iterations: 3 \\
		Learning strategy: 2\\
		Mito agglomeration: Off~~~~~~ \\  
		Threshold: 0.0\\~\\
	\end{tabular}
	&
	\begin{tabular}{l}
		\vspace{0.2mm} \\
		\midrule
		\emph{Results---Test Set} \\ \midrule Cost [m]: 217 \\ Val. acc.: 0.99 \\ Test. acc.: 0.68 \\ Prec./Recall: 0.58/0.56 \\ F1 Score: 0.54 \\
	\end{tabular}
%	\bottomrule
\end{tabular}
\hrule
}
\label{tab:parameters}
\end{table}

@@

Each study session began with a five minute standardized explanation of the task. Then, the participants were asked to perform a 3 minute proofreading task on separate but representative data using focused proofreading. The participants were allowed to ask questions during this time. The classifier did not matter in this case since the user interface was the same. The experimenter then loaded the AC4 subvolume with initial pre-computed classifications by either guided proofreading or focused proofreading depending on assignment. After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation~\cite{NASATLX}.
\begin{figure*}[t]
\centering
\includegraphics[width=\linewidth]{ac4trails_combined.pdf}
\caption{Performance comparison of Plaza's focused proofreading (red) and our guided proofreading (blue) on the AC4 subvolume. All measurements are reported as median VI, the lower the better. We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (green line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle. In all cases, guided proofreading yields better results with fewer corrections.}
\label{fig:ac4trails}
\end{figure*}

@@

\paragraph{Evaluation metric.} We measure the similarity between proofread segmentations and the manual `ground truth' labelings using \textit{variation of information} (VI). VI is a measure of the distance between two clusterings, closely related to mutual information (the lower, the better).

### 2017-04-04 paper/arxiv/guidedproofreading_review.tex
Latest updates including supplemental for submission and the arXiv versions.

%\usepackage{cvpr}
\usepackage{iccv}
\usepackage{microtype}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{makecell}

% Include other packages here, before hyperref.

@@

% \cvprfinalcopy % *** Uncomment this line for the final submission

%\def\cvprPaperID{0947} % *** Enter the CVPR Paper ID here
\def\iccvPaperID{0922}
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

@@

\author{Daniel Haehn\\
Institution1\\
Institution1 address\\
{\tt\small haehn@seas.harvard.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

>>>>

%\usepackage{cvpr}
\usepackage{iccv}
\usepackage{microtype}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{authblk}
% Include other packages here, before hyperref.

@@

\iccvfinalcopy % *** Uncomment this line for the final submission

%\def\cvprPaperID{1234} % *** Enter the CVPR Paper ID here
\def\iccvPaperID{1234}
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

@@

\author[1,2]{Daniel Haehn\thanks{Corresponding author,  \url{haehn@seas.harvard.edu}}}
\author[1,2]{Verena Kaynig}
\author[3]{James Tompkin}
\author[2]{Jeff W. Lichtman}
\author[1,2]{Hanspeter Pfister}
\affil[1]{Harvard Paulson School of Engineering and Applied Sciences, Cambridge, MA 02138, USA}
\affil[2]{Harvard Brain Science Center, Cambridge, MA 02138, USA}
\affil[3]{Brown University, Providence, RI 02912, USA}

### 2017-04-04 paper/arxiv/results.tex
Latest updates including supplemental for submission and the arXiv versions.

%We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings. Lower VI scores indicate less distance to the ground truth and a better segmentation. For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
Additional plots are available as supplemental material due to limited space.

@@

\paragraph{L.~Cylinder.} Evaluation was performed on previously unseen sections of the mouse cortex volume from Kasthuri~\etal~\cite{kasthuri2015saturated}. We generated a dataset of 81,184 correct and 8,780 split error patches with respect to the ground truth labeling. Then, we classified each patch by using focused proofreading and guided proofreading, and compare performance (Fig. \ref{fig:pr}). Our method exhibits higher sensitivity and lower fall-out.% for correct and erroneous patches.

%\begin{table}[t]
%\caption{Classifier comparison on an unbalanced test set of the L.~Cylinder volume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
%\resizebox{\linewidth}{!}{
%\begin{tabular}{lrrrr}
%\toprule
% & Precision & Recall & F1 score & Test \# \\ 
%\midrule
%\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
%~~Correct & 0.93 & 0.31 & 0.47 & 81,184 \\ 
%~~Split error & 0.11 & 0.78 & 0.19 & 8,780 \\ 
%\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
%~~Correct & 1.00 & 0.93 & 0.96 & 81,184 \\ 
%~~Split error & 0.61 & 0.96 & 0.74 & 8,780 \\ 
%\bottomrule
%\end{tabular} 
%}
%\label{tab:prcyl}
%\end{table}

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{gfx/roc.pdf}
\caption{Receiver Operating Characteristic curves comparing focused proofreading and guided proofreading automatic correction. We evaluate on unbalanced test sets of the AC4 subvolume (darker colors) and the L. Cylinder volume (lighter colors). Guided proofreading performs better.}
\label{fig:pr}
\end{figure}

@@

%\begin{table}[t]
%\caption{Classifier comparison on correct and split error patches of the AC4 subvolume.}%While the training of our classifier is more expensive, testing accuracy is superior. }
%\resizebox{\linewidth}{!}{
%\begin{tabular}{lrrrr}
%\toprule
%& Precision & Recall & F1 score & Test \# \\ 
%\midrule
%\emph{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
%~~Correct & 0.94 & 0.69 & 0.80 & 3,488 \\ 
%~~Split error & 0.14 & 0.51 & 0.21 & 332 \\ 
%\emph{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
%~~Correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
%~~Split error & 0.54 & 0.95 & 0.69 & 332 \\ 
%\bottomrule
%\end{tabular} 
%}
%\label{tab:prac4}
%\end{table}

@@

\paragraph{Novice performance.} Participants using focused proofreading were able to reduce the median VI of the automatic segmentation to $0.469$ ($SD=0.87$). On average, users viewed $423.4$ corrections and accepted $45.8$.
%, with an average time of $4.9$ seconds per correction. 
Participants using guided proofreading were able to reduce the median VI to $0.424$ ($SD=0.037$). Here, users viewed on average $353.4$ corrections and accepted $106.9$.
%, with an average correction time of $6.2$ seconds. 
While three users of focused proofreading made the initial segmentation worse, all participants using guided proofreading were able to improve it. In comparison to the results of Haehn~\etal, focused and guided proofreading outperform interactive proofreading with Dojo (median VI $0.535$, $SD=0.055$). The slope of VI score per correction (Fig.~\ref{fig:ac4trails}) and average timings (Tab.~\ref{tab:correctiontimes}) show that guided proofreading enables improvements with fewer corrections than the other tools. Interestingly, novice performance decreases after approximately $300$ corrections. There are two explanations for this: user fatigue, and increasing uncertainty during error suggestion from the classifier. %Regarding fatigue, we suggest that future experiments include short breaks after every ten minutes.

\begin{table}[t]
\caption{Average proofreading speed for novice users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP). Our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP, while being slightly slower per correction.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
\makecell{Approach\\(Novice)} & \makecell{Time Per\\Correction (s)} & \makecell{VI Reduction\\Per Minute} & \makecell{Improvement} \\
\midrule
\emph{Dojo} & 30.5 & -0.00200 & $-8.7\times$ \\
%\emph{Dojo Expert?} & xxx & xxx \\
\emph{FP} & 4.9 & 0.00023 & $1.0\times$\\
\emph{GP} & 6.2 & 0.00173 & $7.5\times$\\
\bottomrule
\end{tabular} 
}
\label{tab:correctiontimes}
\end{table}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
\caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across slices of the AC4 subvolume, with different error correction approaches. The variation resulting from performance of FP with automatic selection is $4.5\times$ higher than GP (as indicated by the arrow), with median VI of $1.9$ and $SD=0.496$.}
\label{fig:ac4boxplot}
\end{figure}

@@

%\subsection{Limitations}
%Guided proofreading works on 2D image sections. This enables error correction without a computationally expensive alignment process. However, the output requires an additional (block-)merging step prior to 3D  analysis.

>>>>

Additional plots are available as supplemental material due to limited space.

@@

\paragraph{L.~Cylinder.} Evaluation was performed on previously unseen sections of the mouse cortex volume from Kasthuri~\etal~\cite{kasthuri2015saturated}. We generated a dataset of 81,184 correct and 8,780 split error patches with respect to the ground truth labeling. Then, we classified each patch by using focused proofreading and guided proofreading, and compare performance (Fig. \ref{fig:pr}). Our method exhibits higher sensitivity and lower fall-out.

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{roc.pdf}
\caption{Receiver Operating Characteristic curves comparing focused proofreading and guided proofreading automatic correction. We evaluate on unbalanced test sets of the AC4 subvolume (darker colors) and the L. Cylinder volume (lighter colors). Guided proofreading performs better.}
\label{fig:pr}
\end{figure}

@@

@@

\paragraph{Novice performance.} Participants using focused proofreading were able to reduce the median VI of the automatic segmentation to $0.469$ ($SD=0.87$). On average, users viewed $423.4$ corrections and accepted $45.8$.
Participants using guided proofreading were able to reduce the median VI to $0.424$ ($SD=0.037$). Here, users viewed on average $353.4$ corrections and accepted $106.9$.
While three users of focused proofreading made the initial segmentation worse, all participants using guided proofreading were able to improve it. In comparison to the results of Haehn~\etal, focused and guided proofreading outperform interactive proofreading with Dojo (median VI $0.535$, $SD=0.055$). The slope of VI score per correction (Fig.~\ref{fig:ac4trails}) and average timings (Tab.~\ref{tab:correctiontimes}) show that guided proofreading enables improvements with fewer corrections than the other tools. Interestingly, novice performance decreases after approximately $300$ corrections. There are two explanations for this: user fatigue, and increasing uncertainty during error suggestion from the classifier.

\begin{table}[t]
\caption{Average proofreading speed for novice users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP). Our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP, while being slightly slower per correction.}
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
\makecell{Approach\\(Novice)} & \makecell{Time Per\\Correction (s)} & \makecell{VI Reduction\\Per Minute} & \makecell{Improvement} \\
\midrule
\emph{Dojo} & 30.5 & -0.00200 & $-8.7\times$ \\
%\emph{Dojo Expert?} & xxx & xxx \\
\emph{FP} & 4.9 & 0.00023 & $1.0\times$\\
\emph{GP} & 6.2 & 0.00173 & $7.5\times$\\
\bottomrule
\end{tabular} 
}
\label{tab:correctiontimes}
\end{table}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{ac4boxplot.pdf}
\caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across slices of the AC4 subvolume, with different error correction approaches. The variation resulting from performance of FP with automatic selection is $4.5\times$ higher than GP (as indicated by the arrow), with median VI of $1.9$ and $SD=0.496$.}
\label{fig:ac4boxplot}
\end{figure}

@@

### 2017-04-04 paper/conclusion.tex
Latest updates including supplemental for submission and the arXiv versions.

%The task of automatic cell boundary segmentation is difficult, and trying to improve such segmentations automatically as a post-process through merge and split error correction is, in principle, no different than trying to improve the underlying cell boundary segmentation. Due to the task difficulty, manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. Humans are the bottleneck and minimizing the manual labor is the goal.
%We have trained classifiers to find merge and split errors in automatic segmentations of connectomics data. We then reduce the correction of these errors to simple yes/no decisions. This allows proofreading with better performance than existing systems.
%Our experiments also show that automatic proofreading works. This has the potential to further reduce the manual labor and will be the target of future research. To encourage testing of our proposed architecture and replication of our experiments, we provide our framework and data as free and open research at (link omitted for review).
%Minimizing manual labor is the goal when proofreading large automatic segmentations. Our classifiers suggest potential errors and corrections better than existing systems. This is especially important for novice users. Novices report difficulties when using fully interactive software but are invaluable to proofread the shear amounts of connectomics data.
%Our experiments also show that automatic proofreading works. This has the potential to further reduce human involvement and will be the target of future research. We provide our framework and data as free and open research at (link omitted for review).
Humans are the bottleneck when proofreading segmentation data and minimizing the manual labor is the goal. Our classifiers suggest potential errors and corrections better than existing methods. This reduces the time spent finding and correcting errors.
Our experiments also show that automatic proofreading has potential to further reduce human involvement. This will be the target of future research. We provide our framework and data as free and open research at (link omitted for review).

>>>>

%The task of automatic cell boundary segmentation is difficult, and trying to improve such segmentations automatically as a post-process through merge and split error correction is, in principle, no different than trying to improve the underlying cell boundary segmentation. Due to the task difficulty, manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. Humans are the bottleneck and minimizing the manual labor is the goal.
%We have trained classifiers to find merge and split errors in automatic segmentations of connectomics data. We then reduce the correction of these errors to simple yes/no decisions. This allows proofreading with better performance than existing systems.
%Our experiments also show that automatic proofreading works. This has the potential to further reduce the manual labor and will be the target of future research. To encourage testing of our proposed architecture and replication of our experiments, we provide our framework and data as free and open research at (link omitted for review).
%Minimizing manual labor is the goal when proofreading large automatic segmentations. Our classifiers suggest potential errors and corrections better than existing systems. This is especially important for novice users. Novices report difficulties when using fully interactive software but are invaluable to proofread the shear amounts of connectomics data.
%Our experiments also show that automatic proofreading works. This has the potential to further reduce human involvement and will be the target of future research. We provide our framework and data as free and open research at (link omitted for review).
Humans are the bottleneck when proofreading segmentation data and minimizing the manual labor is the goal. Our classifiers suggest potential errors and corrections better than existing methods. This reduces the time spent finding and correcting errors.
Our experiments also show that automatic proofreading has potential to further reduce human involvement. This will be the target of future research. We provide our framework and data as free and open research at \url{http://rhoana.org/guidedproofreading/}.

\section*{Acknowledgements}
We would like to thank Stephen Plaza for detailed explanations of focused proofreading and Toufiq Parag for the configuration of the NeuroProof classifier.

### 2017-04-04 paper/supplemental/cremi.tex
Latest updates including supplemental for submission and the arXiv versions.

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/cremi_roc_separate_small.pdf}
\caption{Receiver Operating Characteristic curves comparing focused proofreading and guided proofreading automatic correction on the CREMI A/B/C fruit fly subvolumes. Guided proofreading performs better on all three datasets.}
\label{fig:cremi_performance}
\end{figure}

\paragraph{Classification Performance.} Figure~\ref{fig:cremi_performance} compares the  focused proofreading and guided proofreading classifiers on the CREMI A/B/C datasets. Our method exhibits higher sensitivity and lower fall-out.
